14th International Satisfiability Modulo Theories Competition (SMT-COMP 2019): Rules and Procedures

### 2019-04-11 rules/rules19.tex
Rules: Update changes for the incremental track.

  \item {\it Incremental Track.} \todo{Run beyond the first unknown status query}

>>>>

  \item {\it Incremental Track.}
    In previous years, benchmarks were not eligible for the \incremental Track
    if their first \akey{check-sat} command had unknown status.  Similarly, the
    trace executor used to send commands from the benchmark to the solver's
    standard input channel stopped execution at the first \akey{check-sat}
    command with unknown status. This year, benchmarks whose first
    \akey{check-sat} command has unknown status are eligible for the
    \incremental track and trace execution is only stopped before the solver
    completes a benchmark if the execution runs into the time limit.
    \emph{Rationale:} The previous limitations were imposed by the trace
    executor, which now has been extended to support executing solvers on
    benchmarks beyond \akey{check-sat} commands with unknown status.
